\textcolor{red}{Simple} connectome inference using partial correlation from imaging calcium signal

### 2014-06-16 article.tex
add comments

The directivity in the network introduce causal relations through neurons. A directed edge, i.e. $a_{i,j} = 1$ and $a_{j,i} = 0$, means that neuron $i$ causes $j$. The causal mechanism implies that when neuron $i$ is active, also denoted in this paper as a firing event or a burst, neuron $j$ will be afterwards active consequently. The reciprocal phenomenon is only possible when the edge is bidirectionnal, i.e. $a_{i,j} = a_{j,i} = 1$.

>>>>

The directivity in the network introduce causal relations through neurons. A
directed edge, i.e. $a_{i,j} = 1$ and $a_{j,i} = 0$, means that neuron $i$
causes $j$. The causal mechanism implies that when neuron $i$ is active, also
denoted in this paper as a firing event or a burst, neuron $j$ will be
afterwards active consequently \textcolor{red}{AJ: it's not always true if
there is more than one ancestor and not true if the activation is not
systematic.}. The
reciprocal phenomenon is only possible
when the edge is bidirectionnal, i.e. $a_{i,j} = a_{j,i} = 1$.
